Create Regression Data

### 2022-04-26 data-cleaning/08-create-regression-data.Rmd
add anders, small changes close #29

@@

```{r}
justice_level <- justice_level %>% 
  select(case = casename, ddate2,
         justiceid, justicevot, justicemq, justicefem,
         nonftyp2, lcdisdirfem, cirsplit)

@@

```{r}
justice_level <- justice_level %>% 
  mutate(case = str_replace(case, 'v\\.', 'v'),
         case = str_replace_all(case, "(,|’|'|\\)|\\()", ""),
         case = case_when(
           case == "Anders Solicitor of Richland County v Floyd" ~ "Anders v Floyd",
           case == "Ayotte v Planned Parenthood of Northern New England" ~ "Ayotte v PP",
           case == "City of Akron v Akron Center for Rep Health" ~ "City of Akron v Akron Center",
           case == "Hill et al v Colorado" ~ "Hill v Colorado",
           case == "Judy Madsen v Womens Health Center" ~ "Madsen v Womens Health Center",
           case == "NOW v Joseph Scheidler 1994" ~ "NOW v Scheidler 1994",
           case == "Ohio v Akron Center for Reproductive Health" ~ "Ohio v Akron Center",
           case == "Planned Parenthood Assoc of Kansas City MO v Ashcroft Attorn Gen of MO" ~
             "PP v Ashcroft",
           case == "Planned Parenthood of Southeastern Pennsylvania v Casey" ~ "PP v Casey",
           case == "Planned Parenthood of Central MO v Danforth" ~ "PP v Danforth",
           case == "Joseph Scheidler v NOW 2003" ~ "Scheidler v NOW 2003",
           case == "Joseph Scheidler v NOW 2006" ~ "Scheidler v Now 2006",
           case == "Schenck et al v Pro-Choice Network of Western NY" ~
             "Schenck v Pro-Choice Network",
           case == "Thornburgh v American College of Obstetricians and Gynecologists LDEF" ~
             "Thornburgh v American College of OBGYNs",
           case == "Whole Womens Health v Hellerstedt" ~ "WWH v Hellerstedt",
           T ~ case
         ))

@@

```{r}
# start with justice_level bc this df has cases that the case_level does not
# these cases don't have amicus briefs, which is why they aren't in our data
final <- justice_level %>% 
  left_join(., case_level, by = "case") %>% 
  select(case, ddate2:cirsplit, everything())

@@

```{r}
amicus_only <- "amicus-iv-regression-data.csv"
full <- "amicus-iv-regression-data-all-cases.csv"
box_write(final,
          file_name = full,
          dir_id = 158993526875)
```

@@

```{r}
box_write(final,
          file_name = "amicus-iv-regression-data-frame-by-case-amici-only.csv",
          dir_id = 158993526875)
```

>>>>

Cases to exclude and keep:

Exclude: Anders, Connecticut v Menillo, Guste, Hartigan, Joseph Mazurek, Benten, Lambert, Leavitt, Poe v Gerstein

Include: Bellotti 1976, Singleton v Wulff

@@

```{r}
justice_level <- justice_level %>% 
  filter(
    !grepl("Menillo|Guste|Hartigan|Mazurek|Benten|Lambert|Leavitt|Gerstein", casename)) %>% 
  select(case = casename, ddate2,
         justiceid, justicevot, justicemq, justicefem,
         nonftyp2, lcdisdirfem, cirsplit,
         cfemam, coppam, pfemam, poppam)

@@

```{r}
justice_level <- justice_level %>% 
  mutate(case = str_replace(case, 'v\\.', 'v'),
         case = str_replace_all(case, "(,|’|'|\\)|\\()", ""),
         case = case_when(
           case == "Anders Solicitor of Richland County v Floyd" ~ "Anders v Floyd",
           case == "Ayotte v Planned Parenthood of Northern New England" ~ "Ayotte v PP",
           case == "City of Akron v Akron Center for Rep Health" ~ "City of Akron v Akron Center",
           case == "Gonzales v Planned Parenthood Federation of America" ~ "Gonzales v PP",
           case == "Hill et al v Colorado" ~ "Hill v Colorado",
           case == "Judy Madsen v Womens Health Center" ~ "Madsen v Womens Health Center",
           case == "NOW v Joseph Scheidler 1994" ~ "NOW v Scheidler 1994",
           case == "Ohio v Akron Center for Reproductive Health" ~ "Ohio v Akron Center",
           case == "Planned Parenthood Assoc of Kansas City MO v Ashcroft Attorn Gen of MO" ~
             "PP v Ashcroft",
           case == "Planned Parenthood of Southeastern Pennsylvania v Casey" ~ "PP v Casey",
           case == "Planned Parenthood of Central MO v Danforth" ~ "PP v Danforth",
           case == "Joseph Scheidler v NOW 2003" ~ "Scheidler v NOW 2003",
           case == "Joseph Scheidler v NOW 2006" ~ "Scheidler v Now 2006",
           case == "Schenck et al v Pro-Choice Network of Western NY" ~
             "Schenck v Pro-Choice Network",
           case == "Thornburgh v American College of Obstetricians and Gynecologists LDEF" ~
             "Thornburgh v American College of OBGYNs",
           case == "Whole Womens Health v Hellerstedt" ~ "WWH v Hellerstedt",
           T ~ case
         ))

@@

```{r}
# start with justice_level bc this df has cases that the case_level does not
# these cases don't have amicus briefs, which is why they aren't in our data
final <- justice_level %>% 
  left_join(., case_level, by = "case") %>% 
  select(case, ddate2:poppam, everything())

@@

```{r}
#amicus_only <- "amicus-iv-regression-data.csv"
#full <- "amicus-iv-regression-data-all-cases.csv"
final_case <- "amicus-iv-regression-data-final-cases.csv"
box_write(final,
          file_name = final_case,
          dir_id = 158993526875)
```

@@

```{r}
box_write(final,
          file_name = "amicus-iv-regression-data-frame-by-case-final-cases.csv",
          dir_id = 158993526875)
```

# Two measures per frame: fem and opp

Instead of looking at use of frame across all amici, separate into fem and opp, and then aggregate

# sum up frequencies by frameXparty
case_party_level <- case_amici_level %>% 
  mutate(party = ifelse(grepl("auf", author_type), "fem", "opp")) %>% 
  group_by(case, party) %>% 
  summarize(across(contains("freq"), ~ sum(.x, na.rm = TRUE)))

# reorg
case_party_level <- case_party_level %>% 
  rename_with(.cols=contains("freq"), .fn=~sub("_freq.*", "", .x)) %>% 
  pivot_wider(., c(case,party),
              names_from = party,
              values_from=c(abortion_different:womens_rights),
              names_glue = "{party}_{.value}") %>% 
  select(case, sort(colnames(.)))

final <- justice_level %>% 
  left_join(., case_party_level, by = "case") %>% 
  select(case, ddate2:poppam, everything())
```

```{r}
box_write(final,
          file_name = "amicus-iv-regression-data-frame-by-party-case-final-cases.csv",
          dir_id = 158993526875)
```
